Market simulator

### 2020-10-08 analysis/05_market_simulator.Rmd
finished persona 1 input selected values

# Importance of religion
selectInput(
  "per1_religion_importance",
  label = "Importance of religion:",
  choices = c("Not important", "Important"),
  # selected = "Important",
  width = "450px"
)

# Religion
selectInput(
  "per1_religion",
  label = "Religion:",
  choices = c(
    'Catholic',
    'Protestant',
    'Christian Orthodox',
    'Jewish',
    'Muslim',
    'Sikh',
    'Hindu',
    'Buddhist',
    'Atheist',
    'Other religion'
  ),
  # selected = 'Protestant',
  width = "450px"
)

# Importance of trusting charities
selectInput(
  "per1_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  # selected = "Somewhat unimportant",
  width = "450px"
)

# Trust in charities
selectInput(
  "per1_trust_in_charity",
  label = "Charity Trust:",
  choices = c(
    "No trust at all in charities",
    "Very little trust in charities",
    "Little trust in charities",
    "Neutral trust in charities",
    "Some trust in charities",
    "A lot of trust in charities",
    "Complete trust in charities"
  ),
  # selected = "Complete trust in charities",
  width = "450px"
)

# Donation frequency
selectInput(
  "per1_donation_frequency",
  label = "Donation Frequency:",
  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
  # selected = "Donate at least once a month",
  width = "450px"
)

# Donated last year
selectInput(
  "per1_donation_amount",
  label = "Donation Amount Last Year:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  # selected = "$100-$499",
  width = "450px"
)

# Volunteered in past 12 months
selectInput(
  "per1_volunteer_12",
  label = "Volunteered in last 12 Months:",
  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
  # selected = "Volunteered in past 12 months",
  width = "450px"
)

# Volunteer frequency
selectInput(
  "per1_volunteer_frequency",
  label = "Volunteer Frequency:",
  choices = c(
    "Haven't volunteered in past 12 months",
    "Rarely volunteer",
    "Volunteer more than once a month, less than once a year",
    "Volunteer at least once a month"
  ),
  # selected = "Volunteer at least once a month",
  width = "450px"
)

# History of activism
selectInput(
  "per1_personal_activism",
  label = "Personal Activism:",
  choices = c('Not personally involved', 'Personally involved'),
  # selected = "Personally involved",
  width = "450px"
)

# History of family activism
selectInput(
  "per1_family_activism",
  label = "Family Activism:",
  choices = c('Family not involved', 'Family involved'),
  # selected = "Family involved",
  width = "450px"
)

# Church or religious organization
selectInput(
  "per1_religious_member",
  label = "Church Membership:",
  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
  # selected = "Don't belong to church",
  width = "450px"
)

# Sport or recreational organization
selectInput(
  "per1_sport_member",
  label = "Sport or Recreational Membership:",
  choices = c(
    "Don't belong to sports or rec organization", 
    'Inactive sports or rec organization member',
    'Active sports or rec organization member'
  ),
  # selected = "Don't belong to sports or rec organization",
  width = "450px"
)

# Art, music, or educational organization
selectInput(
  "per1_art_member",
  label = "Art, Music, or Educational Membership:",
  choices = c(
    "Don't belong to educational organization",
    'Inactive art, music, or educational organization member',
    'Active art, music, or educational organization member'
  ),
  # selected = "Don't belong to educational organization",
  width = "450px"
)

# Labor union
selectInput(
  "per1_labor_member",
  label = "Labor Union Membership:",
  choices = c("Don't belong to union", 'Inactive union member', 'Active union member'),
  # selected = "Don't belong to union",
  width = "450px"
)

# Political party
selectInput(
  "per1_political_member",
  label = "Political Party Membership:",
  choices = c(
    "Don't belong to political party",
    'Inactive political party member',
    'Active political party member'
  ),
  # selected = "Active political party member",
  width = "450px"
)

# Environmental organization
selectInput(
  "per1_environmental_member",
  label = "Environmental Organization Membership:",
  choices = c(
    "Don't belong to environmental organization",
    'Inactive environmental organization member',
    'Active environmental organization member'
  ),
  # selected = "Don't belong to environmental organization",
  width = "450px"
)

# Professional association
selectInput(
  "per1_professional_member",
  label = "Professional Association Membership:",
  choices = c(
    "Don't belong to professional association",
    'Inactive professional association member',
    'Active professional association member'
  ),
  # selected = "Don't belong to professional association",
  width = "450px"
)

# Humanitarian or charitable organization
selectInput(
  "per1_humanitarian_member",
  label = "Humanitarian or Charitable Organization Membership:",
  choices = c(
    "Don't belong to humanitarian or charitable organization",
    'Inactive humanitarian or charitable organization member',
    'Active humanitarian or charitable organization member'
  ),
  # selected = "Active humanitarian or charitable organization member",
  width = "450px"
)

# Consumer organization
selectInput(
  "per1_consumer_member",
  label = "Consumer Organization Membership:",
  choices = c(
    "Don't belong to consumer organization",
    'Inactive consumer organization member',
    'Active consumer organization member'
  ),
  # selected = "Don't belong to consumer organization",
  width = "450px"
)

# Other organization
selectInput(
  "per1_other_member",
  label = "Other Organization Membership:",
  choices = c(
    "Don't belong to another organization",
    'Inactive member in another organization',
    'Active member in another organization'
  ),
  # selected = "Don't belong to another organization",
  width = "450px"
)

# Gender
selectInput(
  "per1_gender",
  label = "Gender:",
  choices = c(
    "Male",
    "Female",
    "Transgender",
    "Prefer not to say",
    "Other gender"
  ),
  # selected = "Male",
  width = "450px"
)

# Marital status
selectInput(
  "per1_marital_status",
  label = "Marital Status:",
  choices = c(
    "Married",
    "Widowed",
    "Divorced",
    "Separated",
    "Never married"
  ),
  # selected = "Married",
  width = "450px"
)

# Education
selectInput(
  "per1_education",
  label = "Education:",
  choices = c(
    "Less than high school",
    "High school graduate",
    "Some college",
    "2 year degree",
    "4 year degree",
    "Graduate or professional degree",
    "Doctorate"
  ),
  # selected = "2 year degree",
  width = "450px"
)

# Income
selectInput(
  "per1_income",
  label = "Income:",
  choices = c('Less than median of $61,372', 'More than median of $61,372'),
  # selected = "More than median of $61,372",
  width = "450px"
)

@@

# Age
selectInput(
  "per1_age",
  label = "Age:",
  choices = c('Less than median age of 36', "More than median age of 36"),
  # selected = "Less than median age of 36",
  width = "450px"
)
```

>>>>

# Importance of religion
selectInput(
  "per1_religion_importance",
  label = "Importance of religion:",
  choices = c("Not important", "Important"),
  # selected = "Important",
  selected = ifelse(
    sum(persona_data[35,2]) == 0, "Not important",
    as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
  ),
  width = "450px"
)

# Religion
selectInput(
  "per1_religion",
  label = "Religion:",
  choices = c(
    "Catholic",
    'Protestant',
    'Christian Orthodox',
    'Jewish',
    'Muslim',
    'Sikh',
    'Hindu',
    'Buddhist',
    'Atheist',
    'Other religion'
  ),
  # selected = 'Protestant',
  selected = ifelse(
    sum(persona_data[36:44,2]) == 0, "Catholic",
    as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
  ),
  width = "450px"
)

# Importance of trusting charities
selectInput(
  "per1_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  # selected = "Somewhat unimportant",
  selected = ifelse(
    sum(persona_data[45:50,2]) == 0, "Not at all important",
    as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
  ),
  width = "450px"
)

# Trust in charities
selectInput(
  "per1_trust_in_charity",
  label = "Charity Trust:",
  choices = c(
    "No trust at all in charities",
    "Very little trust in charities",
    "Little trust in charities",
    "Neutral trust in charities",
    "Some trust in charities",
    "A lot of trust in charities",
    "Complete trust in charities"
  ),
  # selected = "Complete trust in charities",
  selected = ifelse(
    sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
    as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
  ),
  width = "450px"
)

# Donation frequency
selectInput(
  "per1_donation_frequency",
  label = "Donation Frequency:",
  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
  # selected = "Donate at least once a month",
  selected = ifelse(
    sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
    as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
  ),
  width = "450px"
)

# Donated last year
selectInput(
  "per1_donation_amount",
  label = "Donation Amount Last Year:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  # selected = "$100-$499",
  selected = ifelse(
    sum(persona_data[58:63,2]) == 0, "$1-$49",
    as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
  ),
  width = "450px"
)

# Volunteered in past 12 months
selectInput(
  "per1_volunteer_12",
  label = "Volunteered in last 12 Months:",
  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
  # selected = "Volunteered in past 12 months",
  selected = ifelse(
    sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
    as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
  ),
  width = "450px"
)

# Volunteer frequency
selectInput(
  "per1_volunteer_frequency",
  label = "Volunteer Frequency:",
  choices = c(
    "Haven't volunteered in past 12 months",
    "Rarely volunteer",
    "Volunteer more than once a month, less than once a year",
    "Volunteer at least once a month"
  ),
  # selected = "Volunteer at least once a month",
  selected = ifelse(
    sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
    as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
  ),
  width = "450px"
)

# History of activism
selectInput(
  "per1_personal_activism",
  label = "Personal Activism:",
  choices = c('Not personally involved', 'Personally involved'),
  # selected = "Personally involved",
  selected = ifelse(
    sum(persona_data[68,2]) == 0, "Not personally involved",
    as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
  ),
  width = "450px"
)

# History of family activism
selectInput(
  "per1_family_activism",
  label = "Family Activism:",
  choices = c('Family not involved', 'Family involved'),
  # selected = "Family involved",
  selected = ifelse(
    sum(persona_data[69,2]) == 0, "Family not involved",
    as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
  ),
  width = "450px"
)

# Church or religious organization
selectInput(
  "per1_religious_member",
  label = "Church Membership:",
  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
  # selected = "Don't belong to church",
  selected = ifelse(
    sum(persona_data[70:71,2]) == 0, "Don't belong to church",
    as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
  ),
  width = "450px"
)

# Sport or recreational organization
selectInput(
  "per1_sport_member",
  label = "Sport or Recreational Membership:",
  choices = c(
    "Don't belong to sports or rec organization", 
    'Inactive sports or rec organization member',
    'Active sports or rec organization member'
  ),
  # selected = "Don't belong to sports or rec organization",
  selected = ifelse(
    sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
    as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
  ),
  width = "450px"
)

# Art, music, or educational organization
selectInput(
  "per1_art_member",
  label = "Art, Music, or Educational Membership:",
  choices = c(
    "Don't belong to educational organization",
    'Inactive art, music, or educational organization member',
    'Active art, music, or educational organization member'
  ),
  # selected = "Don't belong to educational organization",
  selected = ifelse(
    sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
    as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
  ),
  width = "450px"
)

# Labor union
selectInput(
  "per1_labor_member",
  label = "Labor Union Membership:",
  choices = c(
    "Don't belong to union",
    'Inactive union member', 
    'Active union member'
  ),
  # selected = "Don't belong to union",
  selected = ifelse(
    sum(persona_data[76:77,2]) == 0, "Don't belong to union",
    as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
  ),
  width = "450px"
)

# Political party
selectInput(
  "per1_political_member",
  label = "Political Party Membership:",
  choices = c(
    "Don't belong to political party",
    'Inactive political party member',
    'Active political party member'
  ),
  # selected = "Active political party member",
  selected = ifelse(
    sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
    as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
  ),
  width = "450px"
)

# Environmental organization
selectInput(
  "per1_environmental_member",
  label = "Environmental Organization Membership:",
  choices = c(
    "Don't belong to environmental organization",
    'Inactive environmental organization member',
    'Active environmental organization member'
  ),
  # selected = "Don't belong to environmental organization",
  selected = ifelse(
    sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
    as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
  ),
  width = "450px"
)

# Professional association
selectInput(
  "per1_professional_member",
  label = "Professional Association Membership:",
  choices = c(
    "Don't belong to professional association",
    'Inactive professional association member',
    'Active professional association member'
  ),
  # selected = "Don't belong to professional association",
  selected = ifelse(
    sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
    as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
  ),
  width = "450px"
)

# Humanitarian or charitable organization
selectInput(
  "per1_humanitarian_member",
  label = "Humanitarian or Charitable Organization Membership:",
  choices = c(
    "Don't belong to humanitarian or charitable organization",
    'Inactive humanitarian or charitable organization member',
    'Active humanitarian or charitable organization member'
  ),
  # selected = "Active humanitarian or charitable organization member",
  selected = ifelse(
    sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
    as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
  ),
  width = "450px"
)

# Consumer organization
selectInput(
  "per1_consumer_member",
  label = "Consumer Organization Membership:",
  choices = c(
    "Don't belong to consumer organization",
    'Inactive consumer organization member',
    'Active consumer organization member'
  ),
  # selected = "Don't belong to consumer organization",
  selected = ifelse(
    sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
    as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
  ),
  width = "450px"
)

# Other organization
selectInput(
  "per1_other_member",
  label = "Other Organization Membership:",
  choices = c(
    "Don't belong to another organization",
    'Inactive member in another organization',
    'Active member in another organization'
  ),
  # selected = "Don't belong to another organization",
  selected = ifelse(
    sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
    as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
  ),
  width = "450px"
)

# Gender
selectInput(
  "per1_gender",
  label = "Gender:",
  choices = c(
    "Male",
    "Female",
    "Transgender",
    "Prefer not to say",
    "Other gender"
  ),
  # selected = "Male",
  selected = ifelse(
    sum(persona_data[90:93,2]) == 0, "Male",
    as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
  ),
  width = "450px"
)

# Marital status
selectInput(
  "per1_marital_status",
  label = "Marital Status:",
  choices = c(
    "Married",
    "Widowed",
    "Divorced",
    "Separated",
    "Never married"
  ),
  # selected = "Married",
  selected = ifelse(
    sum(persona_data[94:97,2]) == 0, "Married",
    as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
  ),
  width = "450px"
)

# Education
selectInput(
  "per1_education",
  label = "Education:",
  choices = c(
    "Less than high school",
    "High school graduate",
    "Some college",
    "2 year degree",
    "4 year degree",
    "Graduate or professional degree",
    "Doctorate"
  ),
  # selected = "2 year degree",
  selected = ifelse(
    sum(persona_data[98:103,2]) == 0, "Less than high school",
    as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
  ),
  width = "450px"
)

# Income
selectInput(
  "per1_income",
  label = "Income:",
  choices = c('Less than median of $61,372', 'More than median of $61,372'),
  # selected = "More than median of $61,372",
  selected = ifelse(
    sum(persona_data[104,2]) == 0, "Less than median of $61,372",
    as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
  ),
  width = "450px"
)

@@

# Age
selectInput(
  "per1_age",
  label = "Age:",
  choices = c('Less than median age of 36', "More than median age of 36"),
  # selected = "Less than median age of 36",
  selected = ifelse(
    sum(persona_data[111,2]) == 0, "Less than median age of 36",
    as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
  ),
  width = "450px"
)
```
